Considering scale in multilayer animal social networks

### 2020-08-25 paper/manuscript.Rmd
specify fix rate again

### Network layer construction
We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. 
Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
data, the chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes at each time step. As such, individuals in a group are within
the social distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment based on the chain rule
has previously been applied to caribou using a temporal threshold of 5 minutes
and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, individual caribou were represented as nodes and associations between
individuals were represented as edges. We weighted edges by the strength of 
association between individuals using the simple ratio index [SRI, @Cairns_1987].

>>>>

### Network layer construction
We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. 
Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. The chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes collected at each two hour time step. As such, individuals in a group are within
the social distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment is defined using a 
temporal threshold of 5 minutes
and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. 
In all networks, individual caribou were represented as nodes and associations between
individuals were represented as edges. We weighted edges by the strength of 
association between individuals using the simple ratio index [SRI, @Cairns_1987].
